Cartogram Mapping and its Application to Cancer Data Visualisation

### 2019-07-19 review_article.Rmd
edit intro to public face section.

---
title: "Cartogram Mapping and its Application to Cancer Data Visualisation"
author: "Stephanie Kobakian, Jessie Roberts and Dianne Cook"
bibliography: reviewbib.bib
output: 
  pdf_document:
    toc: true
    toc_depth: 2
    number_sections: true
  html_document: default
fontsize: 11pt
link-citations: true
fig_caption: yes
yolo: true
biblio-style: vancouver
---

@@

A grey literature review conducted by (ref) identified 33 publicly available cancer atlases published on the internet between 01/01/2010 to 11/11/2015. Reflecting the high use of chloropleth maps founds in the literature, outlined in the section above, all the public facing maps identified in this review were also chloropleth maps.

### Publishers {-}

The majority of atlases were published by non-commercial organisations, including not-for-profits (NFPs), government, research organisations, advocacy groups or a partnership between an NFP & government. Only one map was published by a commercial entity (Maps of Cancer Mortality Rates in Spain), in this case a media organisation El Pais^[https://elpais.com/].

@@

\newpage
Table: (\#tab:measures) Measures used to report cancer statistics

>>>>

---
title: "Cartogram Mapping and its Application to Cancer Data Visualisation"
author: "Stephanie Kobakian, Jessie Roberts and Dianne Cook"
bibliography: reviewbib.bib
output: 
  html_document: default
  pdf_document:
    toc: true
    toc_depth: 2
    number_sections: true
fontsize: 11pt
link-citations: true
fig_caption: yes
yolo: true
biblio-style: vancouver
---

@@

Cancer maps are effective communication tools for a general or non-expert audience and are commonly used in the public domain to communicate the output of sophisticated statistical analyses to these audiences. The heavy use of chloroplet maps within the research literature is reflected in the types of maps that are found in the public domain. A grey literature review conducted by (ref) identified 33 cancer atlases published on the internet between 01/01/2010 to 11/11/2015 all of which were chloropleth maps. These maps were mostly published by non-commercial organisations, including not-for-profits (NFPs), government, research organisations, advocacy groups or a partnership between an NFP & government. Only one map was published by a commercial entity (Maps of Cancer Mortality Rates in Spain), published by the media organisation El Pais^[https://elpais.com/].

@@

Table: (\#tab:measures) Measures used to report cancer statistics
